How to \underline{not} write Virtual Machines for \mbox{Dynamic Languages}

### 2007-07-26 talk/dyla2007/talk.tex
is this better?
this?
try to make "dynamic languages" be both in the second line in the title.
* birkenfeld sure knows LaTeX - fix title. * an introduction slide.

\title{How to \emph{not} write Virtual Machines for Dynamic Languages}

@@

\begin{frame}
  \frametitle{Introduction}
  \begin{itemize}
  \item XXX intro, talk about scope
  \end{itemize}
\end{frame}

>>>>

\title{How to \underline{not} write Virtual Machines for \mbox{Dynamic Languages}}

@@

\begin{frame}
  \frametitle{Scope}
  This talk is about:

  \begin{itemize}
  \item
    implementing dynamic languages \par(with a focus on complicated ones)
  \item
    in a context of limited resources \par(academic, open source, or
    domain-specific)
  \end{itemize}
  \pause
  \begin{block}{
    Our point}
    \begin{itemize}
    \item
      Do not write virtual machines ``by hand''
    \item
      Instead, write interpreters in high-level languages
    \item
      Meta-programming is your friend
    \end{itemize}
  \end{block}
\end{frame}
